\Large \bf Uncovering Distributed Storage System Bugs during\\Testing (not Production!)

### 2015-09-21 experience.tex
various fixes
updated for rest of Cheng's feedback

The Live Azure Table Migration (MigratingTable) is a library for \emph{transparently migrating} a data set between tables in an Azure Storage service \emph{while} an application is accessing this data set. This case study is particularly interesting because its developers \emph{co-developed} the system with its \psharp model to increase confidence in the former's implementation. Indeed, this co-development process resulted in many tricky bugs discovered before the system went into production (see \S\ref{sec:eval}). The MigratingTable modeling effort differs from the vNext case study: the vNext developers focused on specifying a single liveness property; whereas the MigratingTable developers had to write many complex safety properties. MigratingTable is also interesting because it heavily uses the \texttt{async} and \texttt{await} \csharp 5.0 primitives, which were not originally supported in \psharp. To be able to test MigratingTable, as well as other systems written in \csharp 5.0, we had to extend \psharp with support for intra-machine concurrency (see \S\ref{sec:psharp:testing}).

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{img/mocked_migration}
\caption{Environmental model of MigratingTable (each box with a dotted line represents one \psharp machine).}
\label{fig:mockedmigration}
\end{figure}

>>>>

The Live Azure Table Migration (MigratingTable) is a library for \emph{transparently migrating} a data set between tables in an Azure Storage service \emph{while} an application is accessing this data set. This case study is particularly interesting because its developers \emph{co-developed} the system with its \psharp model to increase confidence in the former's implementation. Indeed, this co-development process resulted in many tricky bugs discovered before the system went into production (see \S\ref{sec:eval}). The MigratingTable modeling effort differs from the vNext case study: the vNext developers focused on specifying a single liveness property; whereas the MigratingTable developers had to write many complex safety properties.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{img/mocked_migration}
\caption{Environment model of MigratingTable (each box with a dotted line represents one \psharp machine).}
\label{fig:mockedmigration}
\end{figure}

### 2015-09-21 overview.tex
updated for rest of Cheng's feedback

\textbf{Handling \csharp 5.0 asynchrony}.
The Live Azure Table Migration system (see \S\ref{sec:cases:migration}) heavily uses the \texttt{async} and \texttt{await} \csharp 5.0 language primitives. An \texttt{async} method is able to perform \texttt{await} on a TPL task \emph{without} blocking the current thread. The \csharp compiler achieves this non-blocking behavior by wrapping the code following an \texttt{await} statement in a TPL \emph{task continuation}, and then returning execution to the caller of the \texttt{async} method. The TPL scheduler executes this task continuation when the task being awaited has completed. In principle, this asynchrony can be modeled using the \psharp primitives for machine creation and message passing. However, in our experience, modeling async/await asynchronous code using \psharp is difficult and time consuming, and thus infeasible for large code bases. To tackle this problem, we developed a solution that automatically captures asynchronously created TPL tasks and wraps them in temporary \psharp machines.

Our solution involves using a \emph{custom task scheduler}, during systematic testing with \psharp, instead of the default TPL scheduler. Assuming that the developer does not explicitly change the task scheduler (something extremely uncommon), any TPL tasks spawned in the \psharp program will be scheduled for execution in the \psharp task scheduler. These tasks will be intercepted by our custom task scheduler and wrapped inside a special, available only internally, task-machine. When the \psharp testing engine schedules a task-machine for execution, the corresponding task is unwrapped and executed. This approach works nicely with the \texttt{async} and \texttt{await} \csharp 5.0 primitives: when an \texttt{async} method is called, the asynchronous TPL task will be automatically wrapped in a task-machine and scheduled by \psharp; for \texttt{await}, no special treatment is required since the task continuation will also be automatically wrapped and scheduled accordingly.

>>>>

\textbf{Handling \csharp 5.0 asynchrony}.
Our case studies heavily use the \texttt{async} and \texttt{await} \csharp 5.0 language primitives. An \texttt{async} method is able to perform \texttt{await} on a TPL task \emph{without} blocking the current thread. The \csharp compiler achieves this non-blocking behavior by wrapping the code following an \texttt{await} statement in a TPL \emph{task continuation}, and then returning execution to the caller of the \texttt{async} method. The TPL scheduler executes this task continuation when the task being awaited has completed. In principle, this asynchrony can be modeled using the \psharp primitives for machine creation and message passing. However, in our experience, modeling async/await asynchronous code using \psharp is difficult and time consuming, and thus infeasible for large code bases. To tackle this problem, we developed a solution that automatically captures asynchronously created TPL tasks and wraps them in temporary \psharp machines.

%The \texttt{async} and \texttt{await} \csharp 5.0 primitives were not originally supported in \psharp. To be able to test our case studies, as well as other systems written in \csharp 5.0, we had to extend \psharp with support for intra-machine concurrency (see \S\ref{sec:psharp:testing}).

Our solution involves using a \emph{custom task scheduler}, during systematic testing with \psharp, instead of the default TPL scheduler.
%Assuming that the developer does not explicitly change the task scheduler (something extremely uncommon),
All TPL tasks spawned in the \psharp program will be scheduled for execution in the \psharp task scheduler. These tasks will be intercepted by our custom task scheduler and wrapped inside a special (not available to the programmer) task-machine. When the \psharp testing engine schedules a task-machine for execution, the corresponding task is unwrapped and executed. This approach works nicely with the \texttt{async} and \texttt{await} \csharp 5.0 primitives: when an \texttt{async} method is called, the asynchronous TPL task will be automatically wrapped in a task-machine and scheduled by \psharp; for \texttt{await}, no special treatment is required since the task continuation will also be automatically wrapped and scheduled accordingly.
